
\subsection{Overview}

The {\tt \modelName} model creates simple solid objects, such as
spheres and boxes.  The solids have mass, and will interact with
other objects.

\subsection{\libgazebo Interfaces}

{\tt \modelName} does not support any interfaces.


\subsection{Player Drivers}

There are no Player drivers for {\tt \modelName}.


\subsection{World File Attributes}

{\tt \modelName} models can be instantiated using the
\verb+<model:SimpleSolid>+ tag.  The following attributes are
supported.

\begin{xmlattrtable}{model}{SimpleSolid}
\modeldefaults
\xmlattr{shape}{string}{NULL}{Shape description.  
Can be any of: {\tt sphere}, {\tt box}, {\tt cylinder}.}
\xmlattr{size}{float}{1.0}{Sphere diameter.}
\xmlattr{size}{tuple}{(0.1, 1.0)}{Cylinder diameter and height.}
\xmlattr{size}{tuple}{(1.0, 1.0, 1.0)}{Box width, length and height.}
\xmlattr{mass}{float}{1.0}{Mass of the object (kg).}
\xmlattr{color}{tuple}{(0, 0, 0, 1)}{Color of the object (including alpha, if transparency is enabled.}
\xmlattr{retro}{float}{0}{Retro-reflectivity level (0 $=$ not a retro-reflector, 1 $=$ perfect retro-reflector).}
\xmlattr{fiducial}{integer}{-1}{Fiducial ID (-1 $=$ not a fiducial).}
\xmlattr{transparent}{true/false}{false}{Sets transparency.}
\xmlattr{texture2D}{string}{NULL}{Texture image filename}
\xmlattr{cfm}{double}{0.01}{Constraint Force Mixing parameter}
\end{xmlattrtable}


\subsection{Body Attributes}

The following bodies are used by this model.

\begin{bodyattrtable}
\bodydefaults
\end{bodyattrtable}



